Data analysis for employee cluster assessment

### 2023-07-14 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Got gap statistic visualization working, wrote helper functions for elbow, silhouette, and gap statistic

@@

```{r}
clusterings %>% 
  ggplot(aes(x = k, y = tot.withinss, color = specification)) +
  geom_line() +
  geom_point() +
  facet_wrap(facets = vars(specification),
             scales = "free")

@@

@@

@@

```{r}
v %>% #count(specification)
  filter(specification == params$in_specification) %>% 
  .$fviz_cluster
```

>>>>

### Making elbow visualizations

```{r}
make_elbow_d <- function(in_specification,
                         in_scale_or_rank,
                         in_working_or_observation_window,
                         in_weekday_correlation)
{
  d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation
    ) %>%
    select(where(is.numeric)) %>%
    fviz_nbclust(., kmeans, method = "wss") +
    theme_fivethirtyeight()
}

### Making silhouette visualizations

```{r}
make_silhouette_d <- function(in_specification,
                              in_scale_or_rank,
                              in_working_or_observation_window,
                              in_weekday_correlation)
{
  d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation
    ) %>%
    select(where(is.numeric)) %>%
    fviz_nbclust(., kmeans, method = "silhouette") +
    theme_fivethirtyeight()
}

### Making gap statistic visualizations

```{r}
make_gap_stat_d <- function(in_specification,
                              in_scale_or_rank,
                              in_working_or_observation_window,
                              in_weekday_correlation)
{
  d %>%
    select_cluster_cols(
      in_scale_or_rank = in_scale_or_rank,
      in_working_or_observation_window = in_working_or_observation_window,
      in_weekday_correlation = in_weekday_correlation
    ) %>%
    select(where(is.numeric)) %>%
    fviz_nbclust(.,  kmeans, 
               nstart = 25,
               method = "gap_stat", 
               nboot = 10,
               # algorithm="Lloyd",
               algorithm="MacQueen",
               iter.max=200,
               verbose = TRUE) +
    theme_fivethirtyeight()
}

## Create dataframe of all permutations {.tabset .tabset-pills}

@@

```{r}
clusterings %>% 
  ggplot(aes(x = k, y = tot.withinss, color = specification)) +
  geom_line() +
  geom_point() +
  # facet_wrap(facets = vars(specification),
  #            scales = "free") +
  facet_grid(
    rows = "specification",
    scales = "free"
  ) +
  theme(
    legend.position = "none"
  )

@@

```{r}
d %>% 
  select_cluster_cols(in_scale_or_rank = "scale",
                      in_working_or_observation_window = "working",
                      in_weekday_correlation = "correlation telework") %>% 
  select(where(is.numeric)) %>% 
  fviz_nbclust(., kmeans, method = "wss") +
  theme_fivethirtyeight()
```

```{r}
make_elbow_d(in_scale_or_rank = "scale",
                      in_working_or_observation_window = "working",
                      in_weekday_correlation = "correlation telework")
```

### Average silhouette

```{r}
make_silhouette_d(in_scale_or_rank = "scale",
                      in_working_or_observation_window = "working",
                      in_weekday_correlation = "correlation telework")
```

Add underscore to specification.

```{r}
kclusts <- 
  kclusts %>% 
  mutate(
    specification = str_replace_all(specification," ","_")
  )
```

### Gap statistic

```{r}
gc()
d %>% 
  select_cluster_cols(in_scale_or_rank = "scale",
                      in_working_or_observation_window = "working",
                      in_weekday_correlation = "correlation telework") %>% 
  select(where(is.numeric)) %>% 
  fviz_nbclust(.,  kmeans, 
               nstart = 25,
               method = "gap_stat", 
               nboot = 10,
               # algorithm="Lloyd",
               algorithm="MacQueen",
               iter.max=200,
               verbose = TRUE) +
  theme_fivethirtyeight()
```

```{r}
gc()
make_gap_stat_d(in_scale_or_rank = "scale",
                      in_working_or_observation_window = "working",
                      in_weekday_correlation = "correlation telework")
```

@@

#### Create cluster visualizations

@@

```{r}
v %>% 
  filter(specification == params$in_specification) %>% 
  .$fviz_cluster
```
